An Online Visual Loop Closure Detection Method for Indoor Robotic Navigation

### 2014-12-01 latex-spie/article.tex
Results...

Ama sunu muhakkak eklemen gerek; el ile secilen bir maskeye dayanarak sonuc hesapliyorsun dolayisiyla sonuclarda hatalar olabilir. (ornek: the performance shown in Table/figure is  representative as the results are obtained with a manually annotated É.). Daha sonra da goz ile saydigin FP/FN sayilarini verirsin, ki bu sayiyi ben de merak ediyorum. En sonda da asil basarimin video uzerinden degerlendirilecegini yazarsin. (ornek: our demo video provides qualitative loop closure results which may be considered to be more representative for our methodÕs performance).

@@

\subsection{Real-Time Performance}

@@

        %%% BRIGHT PR CURVE
        \begin{subfigure}[b]{0.48\textwidth}
        \centering
         % trim parameters by order: left, bottom, right, top
        \includegraphics[trim = 0mm 0mm 5mm 0mm, clip, width=\textwidth]{figures/pr_bright.eps}    
        \caption{Bright dataset results.}
        \label{subfig:pr_bright}
        \end{subfigure}
        ~ 
        %%% DIM PR CURVE
        \begin{subfigure}[b]{0.48\textwidth}
        \centering
         % trim parameters by order: left, bottom, right, top
        \includegraphics[trim = 0mm 0mm 5mm 0mm, clip, width=\textwidth]{figures/pr_dim.eps}    
        \caption{Dim dataset results.}
        \label{subfig:pr_dim}
        \end{subfigure}
        ~
        %%% DARK PR CURVE
        \begin{subfigure}[b]{0.48\textwidth}
        \centering
         % trim parameters by order: left, bottom, right, top
        \includegraphics[trim = 0mm 0mm 5mm 0mm, clip, width=\textwidth]{figures/pr_dark.eps}    
        \caption{Dark dataset results.}
        \label{subfig:pr_bright}
        \end{subfigure}
        ~ 
        %%% ALL PR CURVE
        \begin{subfigure}[b]{0.48\textwidth}
        \centering
         % trim parameters by order: left, bottom, right, top
        \includegraphics[trim = 0mm 0mm 5mm 0mm, clip, width=\textwidth]{figures/pr_all.eps}    
        \caption{Comparison between datasets.}
        \label{subfig:pr_dim}
        \end{subfigure}

>>>>

The results are obtained by three datasets in which the trajectory of the Kinect mounted moving platform is similar to each Dataset that is created in different lightning conditions: Bright, Dim and Dark. In the first loop, there are no loop closures to detect. To examine the performance of the method, precision vs. recall (PR) curves are calculated for each dataset. Precision is simply the fraction of retrieved instances that are relevant, while recall is the fraction of relevant instances that are retrieved. In other words, there are less false positives when the precision is high, and less false negatives when the recall is high. In loop closing problem, high precision is needed to decrease localization errors of the moving autonomous vehicle. The PR curves are illustrated in Figures \ref{subfig:pr_bright}, \ref{subfig:pr_dim}, \ref{subfig:pr_dark} in which there are compared three different image source that are only graysalce images, only depth images and both. The results show that using both grayscale and depth images gives the best performance in bright and dim datasets.....

%VANGELden
%the performance shown in Table/figure is  representative as the results are obtained with a %manually annotated É.
%our demo video provides qualitative loop closure results which may be considered to be more representative for our methodÕs performance

@@

\subsection{Online Performance}

@@

        %%% BRIGHT PR CURVE
        \begin{subfigure}[b]{0.48\textwidth}
        \centering
         % trim parameters by order: left, bottom, right, top
        \includegraphics[trim = 0mm 0mm 5mm 0mm, clip, width=\textwidth]{figures/pr_bright.eps}    
        \caption{Bright dataset results.}
        \label{subfig:pr_bright}
        \end{subfigure}
        ~ 
        %%% DIM PR CURVE
        \begin{subfigure}[b]{0.48\textwidth}
        \centering
         % trim parameters by order: left, bottom, right, top
        \includegraphics[trim = 0mm 0mm 5mm 0mm, clip, width=\textwidth]{figures/pr_dim.eps}    
        \caption{Dim dataset results.}
        \label{subfig:pr_dim}
        \end{subfigure}
        ~
        %%% DARK PR CURVE
        \begin{subfigure}[b]{0.48\textwidth}
        \centering
         % trim parameters by order: left, bottom, right, top
        \includegraphics[trim = 0mm 0mm 5mm 0mm, clip, width=\textwidth]{figures/pr_dark.eps}    
        \caption{Dark dataset results.}
        \label{subfig:pr_dark}
        \end{subfigure}
        ~ 
        %%% ALL PR CURVE
        \begin{subfigure}[b]{0.48\textwidth}
        \centering
         % trim parameters by order: left, bottom, right, top
        \includegraphics[trim = 0mm 0mm 5mm 0mm, clip, width=\textwidth]{figures/pr_all.eps}    
        \caption{Comparison between datasets.}
        \label{subfig:pr_all}
        \end{subfigure}
